---
title: "Diamond sizes"
date: 2016-08-25
output: html_document
---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
smaller <- diamonds %>% 
  filter(carat <= 2.5)
```


Q.2 Download diamond-sizes.Rmd from https://github.com/hadley/r4ds/tree/master/rmarkdown. Add a section that describes the largest 20 diamonds, including a table that displays their most important attributes.

Answer : 
We have data about `r nrow(diamonds)` diamonds. Only 
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

Let us examine the largest 20 diamods.

```{r , echo = FALSE}

largest_20  <- diamonds %>% 
                arrange(desc(carat)) %>% 
                head(20)

knitr::kable(x = largest_20)

```


Q. 3 Modify diamonds-sizes.Rmd to use comma() to produce nicely formatted output. Also include the percentage of diamonds that are larger than 2.5 carats.

Answer : The table has been reprinted by modifying the "price" attribute tp use comma function
```{r}
comma <- function(x) format(x, digits = 2, big.mark = ",")
largest_20$price <- sapply(largest_20$price, function(x) comma(x))
largest_20
```


The percentage of diamonds that are greater that 2.5 carats is `r comma((nrow(largest_20) / nrow(diamonds)) * 100)` %



Q. 4 Set up a network of chunks where d depends on c and b, and both b and c depend on a. Have each chunk print lubridate::now(), set cache = TRUE, then verify your understanding of caching.


```{r a, echo = TRUE}
lubridate::now()

```

```{r b , cache=TRUE, dependson=c("a"), echo = TRUE}

lubridate::now()

```

```{r c , cache=TRUE, dependson=c("a"), echo = TRUE}

lubridate::now()

```

```{r d, cache=TRUE, dependson=c("b","c"), echo = TRUE}

lubridate::now()

```
