---
title: "ex24.7"
author: "Mrugank"
date: "8/17/2020"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
```

# How diamonds vary by cut, color and clarity?

We will explore the **diamonds** data set in ggplot package to see distribution of diamonds based on different attributes. *Cut, Color and Clarity* are `r  class(diamonds$cut)` variables. A simple bar plot is helpful for visualizing the distribution of a factor variable.


## 1. Cut
*Cut* has levels ordered as `r levels(diamonds$cut)`. 

```{r cut}
ggplot(data = diamonds,mapping = aes(x = cut)) +
  geom_bar()

```

As you can see from the above graph, most of the diamonds fall under the "G" Color category.


## 2. Color
*Colour* has levels ordered as `r levels(diamonds$color)`. 
```{r color}
ggplot(data = diamonds,mapping = aes(x = color)) +
  geom_bar()

```

As you can see from the above graph, most of the diamonds fall under the "Ideal" Cut category.



## 3. Clarity
*Clarity* has levels ordered as `r levels(diamonds$clarity)`. 

```{r clarity}
ggplot(data = diamonds,mapping = aes(x = clarity)) +
  geom_bar()

```

As you can see from the above graph, most of the diamonds fall under the "SI1" Clarity category.
